### 2022-11-20 ms.rmd
Need tp exclude data where V = 0, and also NA because there are no data to calculate

```{r acclimation_cap}
########################
### Differences in acclimation capacity between terrestrial, aquatic and marine
########################
phylo_cor <- vcv(tree_p0.7, cor = TRUE)
## lnRR first
lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name)) %>% mutate(spp = species_full)

model1.1 <- metafor::rma.mv(effect_size, V = V, 
                            random = list(~1 + type | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                            R = list(species_full = phylo_cor), dfs = "contain", test = "t", data = lnRRQ10_data)

>>>>

```{r acclimation_cap}
########################
### Differences in acclimation capacity between terrestrial, aquatic and marine
########################
phylo_cor <- vcv(tree_p0.7, cor = TRUE)

#############
## lnRRQ10
#############

# Subset the data
lnRRQ10_data <- data_long %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0) %>% mutate(spp = species_full)

# Intercept only model. 
model1.1 <- metafor::rma.mv(effect_size ~ type, V = V, 
                            random = list(~1 + type | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                            R = list(species_full = phylo_cor), dfs = "contain", test = "t", data = lnRRQ10_data)
